TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-06-06 paper/draft.tex
describe sections

In particular, the metallicity abundance can be difficult to determine in M dwarfs, as overlapping lines in a spectrum and lack of continuum make it difficult to define features and extract their line strengths. A number of studies focused on improving M dwarf metallicity precisions have used systems of M dwarfs in common proper motion with an FGK star, to developed precise empirical relations (as good as $\sim$0.07\,dex) between the adopted metallicities of the FGK primary (under the assumption kinematically similar pairs are co-evolutionary; \citealt{Bonfils:2005}), and strong, isolated lines in the optical spectra of the M dwarf (e.g. \citealt{Terrien:2012}, \citealt{Rojas-Ayala:2012}, \citealt{Newton:2014}).
However these metallicity calibrations are inaccesible for analysis with \apogee, as the narrow infrared wavelength coverage does not include the relevant calibration indices used by existing studies (such as Ca I or KI lines in the optical), and blending of multiple atomic and molecular species at high resolution makes it impractical to identify and deconvolve new individual features for analysis.

@@

>>>>

A number of studies focused on improving M dwarf metallicity precisions have used systems of M dwarfs in common proper motion with an FGK star, to developed precise empirical relations (as good as $\sim$0.07\,dex) between the adopted metallicities of the FGK primary (under the assumption kinematically similar pairs are co-evolutionary; \citealt{Bonfils:2005}), and strong, isolated lines in the optical spectra of the M dwarf (e.g. \citealt{Terrien:2012}, \citealt{Rojas-Ayala:2012}, \citealt{Newton:2014}).
However these metallicity calibrations are inaccesible for analysis with \apogee, as the narrow infrared wavelength coverage does not include the relevant calibration indices used by existing studies (such as Ca I or KI lines in the optical), and blending of multiple atomic and molecular species at high resolution makes it impractical to identify and deconvolve new individual features for analysis.

@@

This paper is organized as follows: in Section \ref{sec:data} we describe the technical specifications of the data from the APOGEE survey, as well as our sample selection and derivation of training parameters. 
Section \ref{sec:cannon} describes our model implementation using \thecannon framework.
In Section \ref{sec:results} we present our experimental results, evaluate the predictive accuracy of our models, apply our model to a selected test sample of $>10,000$ sources, and examine the validity of our parameters against color-temperature relations and isochrone grids.
Finally, in Section \ref{sec:discussion} we discuss model performance, future improvements, and implications of our results in the context of present/upcoming stellar and exoplanet surveys.
